Modelling and Analysis of an Elevator System with NuSMV2

### 2013-05-30 paper/main.tex
paper: added data

\usepackage{listings}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{float}
\usepackage{xspace}
\usepackage{enumerate}

@@

	% TODO

@@

@@

	Using this bound, BMC is significantly slower, although of course the algorithm can stop earlier once it has found a counterexample for some property. It is exactly as has been stated before: BMC can be useful if one is looking for counterexamples in settings with lots of users and floors, but for exhaustive search a BDD is the better choice.

	\bibliographystyle{plain}
	\bibliography{main}

\end{document}

>>>>

\usepackage{listings}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{float}
\usepackage{xspace}
\usepackage{enumerate}
\usepackage{diagbox}

@@

	\begin{figure}[H]
		\begin{center}
			\begin{tabular}{r|r|r|r|r}
				\backslashbox{$F$}{$n$} & 1 & 2 & 3 & 4 \\ \hline
				2	& 0.028		& 0.053		& 0.220		& 10.151	\\ \hline
				3	& 0.041		& 0.345		& 83.652	&			\\ \hline
				4	& 0.072		& 1.465		&			&			\\ \hline
				5	& 0.142		& 18.114	&			&			\\ \hline
				6	& 0.203		& 56.642	&			&			\\ \hline 
				7	& 0.270		& 204.439	&			&			\\ \hline
				8	& 0.680		&			&			&			\\ \hline
				9	& 0.720		&			&			&			\\ \hline
				10	& 0.970		&			&			&			\\ \hline
				20	& 31.313	&			&			&			\\ \hline
				30	& 56.174	&			&			&			\\ \hline
				40	& 57.226	&			&			&			\\ \hline
				50	& 99.425	&			&			&			\\ \hline
			\end{tabular}
		\end{center}

		\caption{Computation time without \texttt{wants\_to}-feature}
	\end{figure}

	\begin{figure}[H]
		\begin{center}
			\begin{tabular}{r|r|r|r}
				\backslashbox{$F$}{$n$} & 1 & 2 & 3 \\ \hline
				2	& 0.032		& 0.132		& 2.711		\\ \hline
				3	& 0.065		& 4.684		&			\\ \hline
				4	& 0.149		&			&			\\ \hline
				5	& 0.627		&			&			\\ \hline
				6	& 1.285		&			&			\\ \hline 
				7	& 2.211		&			&			\\ \hline
				8	& 3.785		&			&			\\ \hline
				9	& 8.862		&			&			\\ \hline
				10	& 42.684	&			&			\\ \hline
			\end{tabular}
		\end{center}

		\caption{Computation time with \texttt{wants\_to}-feature}
	\end{figure}

@@

	\begin{figure}[H]
		\begin{center}
			\begin{tabular}{r|r|r|r|r|r}
				\backslashbox{$F$}{$n$} & 1 & 2 & 3 & 4 & 5 \\ \hline
				2	& 0.030		& 0.046		& 0.114		& 0.424		& 2.376	\\ \hline
				3	& 0.039		& 0.209		& 2.535		& 53.188	&		\\ \hline
				4	& 0.062		& 0.700		& 15.765	&			&		\\ \hline
				5	& 0.105		& 2.333		&			&			&		\\ \hline
				6	& 0.146		& 4.973		&			&			&		\\ \hline 
				7	& 0.196		& 8.727		&			&			&		\\ \hline
				8	& 0.282		& 14.581	&			&			&		\\ \hline
				9	& 0.427		& 53.658	&			&			&		\\ \hline
				10	& 0.558		& 107.473	&			&			&		\\ \hline
				20	& 2.456		&			&			&			&		\\ \hline
				30	& 8.110		&			&			&			&		\\ \hline
				40	& 19.068	&			&			&			&		\\ \hline
				50	& 63.694	&			&			&			&		\\ \hline
			\end{tabular}
		\end{center}

		\caption{Computation time using \texttt{-t} on empty file without \texttt{wants\_to}-feature}
	\end{figure}

	\begin{figure}[H]
		\begin{center}
			\begin{tabular}{r|r|r|r|r|r}
				\backslashbox{$F$}{$n$} & 1 & 2 & 3 & 4 & 5 \\ \hline
				2	& 0.034		& 0.133		& 0.974		& 8.253		& 115.457	\\ \hline
				3	& 0.066		& 4.528		& 			& 			&			\\ \hline
				4	& 0.178		& 59.415	& 			&			&			\\ \hline
				5	& 0.574		&			&			&			&			\\ \hline
				6	& 1.225		&			&			&			&			\\ \hline 
				7	& 2.164		&			&			&			&			\\ \hline
				8	& 3.830		&			&			&			&			\\ \hline
				9	& 8.426		&			&			&			&			\\ \hline
				10	& 14.296	&			&			&			&			\\ \hline
			\end{tabular}
		\end{center}

		\caption{Computation time using \texttt{-t} on empty file with \texttt{wants\_to}-feature}
	\end{figure}

@@

	Using this bound, BMC is significantly slower, although of course the algorithm can stop earlier once it has found a counterexample for some property. It is exactly as has been stated before: BMC can be useful if one is looking for counterexamples in settings with lots of users and floors, but for exhaustive search a BDD is the better choice.
\end{document}
